Sparse spectral and $p$-finite element methods on disk-slices and trapeziums I: zero boundary conditions

### 2019-04-03 papers/halfdisk/halfdisk.tex
Trapezium appendix

Note that by setting $c = 0$, $\alpha = 0$ and $\beta = 1$ we obtain the 2D orthogonal polynomials on the half disk.

>>>>

Note that by setting $c = 0$, $\alpha = 0$ and $\beta = 1$ we obtain the 2D orthogonal polynomials on the half-disk.

\section{Trapeziums}

We can further extend this work to trapezium shaped domains. Note that for any trapezium there exists an affine map to the canonical trapezium domain that we consider here, given by
\begin{align}
	\Omega := \{(x,y) \in \R^2 \quad | \quad \alpha < x < \beta, \: \gamma \rho(x) < y < \delta \rho(x)\}
\end{align}
with 
\begin{align}
\begin{cases}
(\alpha, \beta) &:= (0,1) \\
(\gamma, \delta) &:= (0,1) \\
\rho(x) &:= 1-\half x \\
w^{(a,b,c)}_H(x) &:= (x - \alpha)^{a} \: (\beta - x)^b \: \rho(x)^{c} = x^a \: (1-x)^{b} \: (1-\half x)^{c} \\
w^{(a,b)}_P(x) &:= (x - \gamma)^a \: (\delta-x)^b.
\end{cases}
\end{align}
The weight $w^{(b)}_2(x)$ is a still an ultraspherical weight, and the corresponding OPs are the Jacobi polynomials $\{P_n^{(b, b)}\}$. $w^{(a,b,c)}_1(x)$ is the (non-classical) weight for the OPs denoted $\{H_n^{(a, b,c)}\}\). Thus we arrive at the two parameter family of 2D orthogonal polynomials $\{\Pnk\}$ on $\Omega$ given by, for \(0 \le k \le n, \: n = 0,1,2,\dots,\)
\begin{align}
	\Pnk^{(a,b,c)}(x,y) := H_{n-k}^{(c, a, b+k+\half)}(x) \: \rho(x)^k \: P_k^{(b,b)}(\frac{y}{\rho(x)}), \quad (x,y) \in \Omega, 
\end{align}
orthogonal with respect to the weight
\begin{align}
	W^{(a,b,c)}(x,y) &:= w^{(a,b,c)}_H(x) w^{(c,d)}_P(\frac{y}{\rho(x)}) \nonumber \\
	&= x^a \: (1-x)^b \: y^c \: (1-\half x - y)^d, \quad (x,y) \in \Omega.
\end{align}
